Q1: Are lake and terrestrial primary productivity coherent?

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12_20200323.Rmd
revisions post review

dbuff[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))]

@@

coh.chlaXaccndvi<-NULL

for(lind in 1:length(analysislakes$lakedata)){
  lakedat.ii<-cleandat(analysislakes$lakedata[[lind]], as.numeric(colnames(analysislakes$lakedata[[lind]])), clev=5)$cdat
  chlaXaccndvi<-coh(lakedat.ii[1,], lakedat.ii[2,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
                    norm="powall", sigmethod="fast", nrand=10000)
  for(rind in 1:nrow(tsranges)){
    chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
  }
  coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
}

@@

save(list=c("coherentlakes.st","coherentlakes.lt"),
     file="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes.RData")

@@

plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
lines(tt,comb1,lwd=2)
lines(tt,comb2,lwd=2,col="red")
axis(1, at=c(0,10,20,30,40,50),labels=NA)
axis(2, at=c(-1,1.5,4), labels=NA)
mtext("Timescale specific relationship",3,line=0.25)
text(0.4,4.9,"a)",cex=1.2)

plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
axis(1, at=c(0,10,20), labels=NA)
axis(2, at=c(-1,0,1), labels=NA)
lines(tt[tt<=20],sig3,lwd=2)
lines(tt[tt<=20],sig4,lwd=2,col="red")
mtext(expression(paste(phi," = 0")))
text(1,0.9,"b)",cex=1.2)

plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
axis(1, at=c(0,10,20), labels=NA)
axis(2, at=c(-1,0,1), labels=NA)
lines(tt[tt<=20],sig3,lwd=2)
lines(tt[tt<=20],sig5,lwd=2,col="red")
mtext(expression(paste(phi," = ",pi,"/2")))
text(1,0.9,"c)",cex=1.2)

plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
axis(1, at=c(0,10,20), labels=NA)
axis(2, at=c(-1,0,1), labels=NA)
lines(tt[tt<=20],sig3,lwd=2)
lines(tt[tt<=20],sig6,lwd=2,col="red")
mtext(expression(paste(phi," = ",pi)))
text(1,0.9,"d)",cex=1.2)

@@

#plotting
tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_distributions_20191031.tif", units="in",
     res=300, width=6.5, height=5)
layout(matrix(1:4,2,2,byrow=T),heights=c(0.4,0.4,0.6,0.6))

@@

par(mar=c(1,1,2,1))
rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phase",
       at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phase",
     at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")

@@

@@

bgcol<-rep("grey",length(lakedata))
bgcol[names(lakedata)=="3370"]<-"red"
bgcol[names(lakedata)=="4386"]<-"cyan3"

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map_plus.tif",units="in",
     res=300, width=6.5, height=2.75)

@@

par(mar=rep(0,4))
plot(lagosstates, main="",bty="o")
points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.7, col="black",bg=bgcol)
legend("bottomright",pch=c(0,21,21,21),col="black",pt.bg=c("grey","grey","red","cyan3"),
       legend=c("States in LAGOS-NE","Selected lakes","Coherent lake","Non-coherent lake"),inset=c(0.025,0.01),bty="n")
text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.06*diff(par("usr")[3:4]),"a)")

@@

cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")

@@

plot(lagosstates, main="Lakes by short timescale coherence")
par()$usr
points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)

plot(lagosstates, main="Lakes by long timescale coherence")
points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_coherencemap.tif", units="in",
     res=300, width=6.5, height=7.5)

layout(laymat)
par(mar=c(0,0,1.5,0))

plot(lagosstates, main="Short timescale coherence")
points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)

plot(lagosstates, main="Long timescale coherence")
points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)

par(mar=c(5,1,5,1))
image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
axis(2,at=seq(0,1,0.2))

@@

@@

#depth
depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth"))
depth<-depth[depth$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,] #use max depth because it's more complete

@@

preds<-analysislakes$lakeinfo[,colnames(analysislakes$lakeinfo) %in% c("lagoslakeid","end","start")]
preds$tslength<-preds$end-preds$start + 1
preds<-left_join(preds, dt.geo, by="lagoslakeid")
preds<-left_join(preds, dt.conn, by="lagoslakeid")
preds<-left_join(preds, dt.chag, by="hu12_zoneid")
preds<-left_join(preds, dt.lulc, by="lagoslakeid")
preds<-left_join(preds, avg.chla, by="lagoslakeid")
preds<-left_join(preds, cv.accndvi, by="lagoslakeid")
preds<-left_join(preds, depth, by="lagoslakeid")
preds<-left_join(preds, shoredev, by="lagoslakeid")
preds<-left_join(preds, dr, by="lagoslakeid")

@@

rfdat.cohst<-left_join(coh.chlaXaccndvi[,c(10,3)], preds)
rfdat.cohst<-rfdat.cohst[,!colnames(rfdat.cohst) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
rfdat.cohst<-rfdat.cohst[,!grepl("borderhu12s",colnames(rfdat.cohst))]

@@

```{r rfCoherence_lt, echo=TRUE, cache=FALSE}
rfdat.cohlt<-left_join(coh.chlaXaccndvi[,c(10,6)], preds)
rfdat.cohlt<-rfdat.cohlt[,!colnames(rfdat.cohlt) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
rfdat.cohlt<-rfdat.cohlt[,!grepl("borderhu12s",colnames(rfdat.cohlt))]

@@

rfdat.phist<-left_join(coh.chlaXaccndvi[,c(10,2)], preds)
rfdat.phist<-rfdat.phist[,!colnames(rfdat.phist) %in% 
                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid")]
rfdat.phist<-rfdat.phist[,!grepl("borderhu12s",colnames(rfdat.phist))]

@@

rfdat.philt<-left_join(coh.chlaXaccndvi[,c(10,5)], preds)
rfdat.philt<-rfdat.philt[,!colnames(rfdat.philt) %in% 
                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid")]
rfdat.philt<-rfdat.philt[,!grepl("borderhu12s",colnames(rfdat.philt))]

@@

print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
ltxt.st<-c("total N deposition","cv(NDVI)","% woody wetlands","all wetlands shoreline","mean runoff",
           "% developed open space","% regime c wetlands","forest wetlands shoreline","mean annual precipitation",
           "shoreline development ratio")

print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
ltxt.lt<-c("% shrub/scrub","cv(NDVI)","% regime f wetlands","mean annual precipitation","forest wetlands shoreline",
           "% cultivated crops","headwaters density","% mixed forest", "wetland shoreline", "% developed low intensity")

print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing = T)][1:10])
ltxt.cosphist<-c("open wetlands shoreline","% open wetlands area","mean chlorophyll-a","% shrub/scrub",
              "% cultivated crops","% developed open space","% developed high intensity","nitrate deposition",
              "groundwater recharge","% open water")

print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing = T)][1:10])
ltxt.sinphilt<-c("open wetlands shoreline", "all wetlands shoreline","% cultivated crops","% regime f wetlands",
                 "% evergreen forest","forested wetlands shoreline", "% open wetlands area","% barren land",
                 "max depth","lake connection type")

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10_iws.tif",units="in",
     res=300,width=6.5, height=5)

@@

barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="a) Short timescale coher.", horiz=T,font.main=1)

barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="c) Long timescale coher.", horiz=T, font.main=1)

barplot(rev(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.cosphist),las=2,
        main=expression(paste("b) Short timescale cosine(",phi,")",sep="")), horiz=T)

barplot(rev(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.sinphilt),las=2,
        main=expression(paste("d) Long timescale sine(",phi,")",sep="")), horiz=T)

>>>>

@@

coh.chlaXaccndvi<-NULL
# surrog.coh<-NULL
# ar1.chla<-NULL
# ar1.ndvi<-NULL

for(lind in 1:length(analysislakes$lakedata)){
  lakedat.ii<-cleandat(analysislakes$lakedata[[lind]], as.numeric(colnames(analysislakes$lakedata[[lind]])), clev=5)$cdat
  chlaXaccndvi<-coh(lakedat.ii[1,], lakedat.ii[2,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
                    norm="powall", sigmethod="fast", nrand=10000)
  # ar1.chla<-c(ar1.chla, arima(lakedat.ii[1,], order=c(1,0,0))$coef[1])
  # ar1.ndvi<-c(ar1.ndvi, arima(lakedat.ii[2,], order=c(1,0,0))$coef[1])

  for(rind in 1:nrow(tsranges)){
    chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
  }
  coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
  ## this following is wrong, need to take Mod after mean
  # surrog.coh<-rbind(surrog.coh,
  #                   cbind(apply(Mod(chlaXaccndvi$signif$scoher[,chlaXaccndvi$timescales<4]),1,mean)
  #                   ,apply(Mod(chlaXaccndvi$signif$scoher[,chlaXaccndvi$timescales>4]),1,mean)
  #                          ))
}

@@

save(list=c("coherentlakes.st","coherentlakes.lt"),
     file="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes_byWatershed.RData")

@@

plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
lines(tt,comb1,lwd=2,col="royalblue")
lines(tt,comb2,lwd=2,col="forestgreen")
axis(1, at=c(0,10,20,30,40,50),labels=NA)
axis(2, at=c(-1,1.5,4), labels=NA)
mtext("Timescale-specific relationship",3,line=0.25)
text(0.4,4.9,"a)",cex=1.2)

plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
axis(1, at=c(0,10,20), labels=NA)
axis(2, at=c(-1,0,1), labels=NA)
lines(tt[tt<=20],sig3,lwd=2, col="royalblue")
lines(tt[tt<=20],sig4,lwd=2,col="forestgreen")
mtext(expression(paste("in-phase (",phi," = 0)")))
text(1,0.9,"b)",cex=1.2)

plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
axis(1, at=c(0,10,20), labels=NA)
axis(2, at=c(-1,0,1), labels=NA)
lines(tt[tt<=20],sig3,lwd=2, col="forestgreen")
lines(tt[tt<=20],sig5,lwd=2,col="royalblue")
mtext(expression(paste("lagged (",phi," = ",pi,"/2)")))
text(1,0.9,"c)",cex=1.2)

plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
axis(1, at=c(0,10,20), labels=NA)
axis(2, at=c(-1,0,1), labels=NA)
lines(tt[tt<=20],sig3,lwd=2, col="royalblue")
lines(tt[tt<=20],sig6,lwd=2,col="forestgreen")
mtext(expression(paste("anti-phase (",phi," = ",pi,")")))
text(1,0.9,"d)",cex=1.2)

@@

# ## ar1 comparison
# coef.chla<-mean(ar1.chla)
# coef.ndvi<-mean(ar1.ndvi)
# tslen<-ceiling(mean(analysislakes$lakeinfo$tslength))
# 
# nreps=1000

# ar1.coh<-NULL
# for(ii in 1:nreps){
# 
#   y1<-cleandat(arima.sim(list(ar=coef.chla), n=tslen, n.start=500),1:tslen,5)$cdat
#   y2<-cleandat(arima.sim(list(ar=coef.ndvi), n=tslen, n.start=500),1:tslen,5)$cdat
#   zz<-coh(y1,y2,1:tslen,norm="powall")
#   ar1.coh<-rbind(ar1.coh,cbind(Mod(mean(zz$coher[zz$timescales<4]))
#                  ,Mod(mean(zz$coher[zz$timescales>4]))))
# 
# }
# 
# hist(ar1.coh[,1])
# hist(ar1.coh[,2])
#plotting
tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_distributions_20200609.tif", units="in",
     res=300, width=6.5, height=5)
layout(matrix(1:4,2,2,byrow=T),heights=c(0.45,0.6,0.45,0.6))

@@

par(mar=c(2,2,3,2))
rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phase",
       at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.9*par()$usr[4],"c)")
mtext("lagged positive",1,col="grey",cex=0.75)
mtext("negative (anti-phase)",2,col="grey",cex=0.75, line=-1.8)
mtext("lagged negative",3,col="grey",cex=0.75)
mtext("positive (in-phase)",4,col="grey",cex=0.75, line=-2)

rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phase",
     at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
text(0.9*par()$usr[1],0.9*par()$usr[4],"d)")
mtext("lagged positive",1,col="grey",cex=0.75)
mtext("negative (anti-phase)",2,col="grey",cex=0.75, line=-1.8)
mtext("lagged negative",3,col="grey",cex=0.75)
mtext("positive (in-phase)",4,col="grey",cex=0.75, line=-2)

@@

mapdata<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid
                    ,gnis_name=analysislakes$lakeinfo$gnis_name
                    ,nhd_lat=analysislakes$lakeinfo$nhd_lat
                    ,nhd_long=analysislakes$lakeinfo$nhd_long)
mapdata<-left_join(mapdata, coh.chlaXaccndvi, by="lagoslakeid")

@@

mapdata$bgcol<-rep("grey",nrow(mapdata))
mapdata$bgcol[mapdata$lagoslakeid==cohid]<-"red"
mapdata$bgcol[mapdata$lagoslakeid==incohid]<-"cyan3"

mapdata$pchar.st<-rep(16,nrow(mapdata))
mapdata$pchar.st[mapdata$accndvip.ts1<0.05]<-21

mapdata$pchar.lt<-rep(16,nrow(mapdata))
mapdata$pchar.lt[mapdata$accndvip.ts2<0.05]<-21

mapdata$ptcex<-rep(0.7, nrow(mapdata))
mapdata$ptcex[mapdata$lagoslakeid==cohid | mapdata$lagoslakeid==incohid]<-1.2

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_map_plus.tif",units="in",
     res=300, width=6.5, height=2.75)

@@

par(mar=rep(0,4))
plot(lagosstates, main="",bty="o")
points(mapdata$nhd_long, mapdata$nhd_lat, pch=21, cex=mapdata$ptcex, col="black",bg=mapdata$bgcol)
legend("bottomright",pch=c(0,21,21,21),col="black",pt.bg=c("grey","grey","red","cyan3"),
       legend=c("States in LAGOS-NE","Selected lakes","Coherent lake","Non-coherent lake"),inset=c(0.025,0.01),bty="n")
text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.06*diff(par("usr")[3:4]),"a)")

@@

#cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")

@@

plot(lagosstates, main="Lakes by short timescale coherence")
par()$usr
points(mapdata$nhd_long[mapdata$accndvip.ts1 >=0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 >=0.05], pch=16, cex=1, 
       col=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 >=0.05],2)*100])
points(mapdata$nhd_long[mapdata$accndvip.ts1 <0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 <0.05], pch=21, cex=1, 
       bg=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 <0.05],2)*100])
colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)

plot(lagosstates, main="Lakes by long timescale coherence")
points(mapdata$nhd_long, mapdata$nhd_lat, pch=16, cex=1, col=pal[round(mapdata$accndvicoh.ts2,2)*100])
colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_coherencemap_st.tif", units="in",
     res=300, width=6.5, height=3.75)

# layout(laymat)
par(mar=c(0.1,0.1,0.1,0.1))

plot(lagosstates, main="")
points(mapdata$nhd_long[mapdata$accndvip.ts1 >=0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 >=0.05], pch=16, cex=1.5, 
       col=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 >=0.05],2)*100])
points(mapdata$nhd_long[mapdata$accndvip.ts1 <0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 <0.05], pch=21, cex=1.5, 
       bg=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 <0.05],2)*100], lwd=1.5)
#colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
#text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)

ext<-par("usr")
par(new=T, mar=c(1.5,0.1,1.5,0.1), plt=c(0.45, 0.95, 0.08,0.13), tcl=-0.3, mgp=c(1,0.5,0))
image(matrix(1:100,ncol=1),col=pal,xaxt="n",yaxt="n")
axis(1,at=seq(0,1,0.2))
mtext(3,"Coherence",line=0)

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS2_coherencemap_lt.tif", units="in",
     res=300, width=6.5, height=3.75)

par(mar=c(0.1,0.1,0.1,0.1))

plot(lagosstates, main="")
points(mapdata$nhd_long[mapdata$accndvip.ts2 >=0.05], mapdata$nhd_lat[mapdata$accndvip.ts2 >=0.05], pch=16, cex=1.5, 
       col=pal[round(mapdata$accndvicoh.ts2[mapdata$accndvip.ts2 >=0.05],2)*100])
points(mapdata$nhd_long[mapdata$accndvip.ts2 <0.05], mapdata$nhd_lat[mapdata$accndvip.ts2 <0.05], pch=21, cex=1.5, 
       bg=pal[round(mapdata$accndvicoh.ts2[mapdata$accndvip.ts2 <0.05],2)*100], lwd=1.5)

ext<-par("usr")
par(new=T, mar=c(1.5,0.1,0.1,0.1), plt=c(0.45, 0.95, 0.08,0.13), tcl=-0.3, mgp=c(1,0.5,0))
image(matrix(1:100,ncol=1),col=pal,xaxt="n",yaxt="n")
axis(1,at=seq(0,1,0.2))
mtext(3,"Coherence")

dev.off()
#colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
#axis(1,at=c(1,100),labels=c(0,1))
#text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)

# par(mar=c(5,1,5,1))
# image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
# axis(2,at=seq(0,1,0.2))

@@

# dt.type<-dt$locus
# dt.type<-dt.type[,colnames(dt.type) %in% c("lagoslakeid","nhd_fcode","nhd_ftype")]
# dt.type<-dt.type[dt.type$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
#125 of 126 lakes are non-reservoirs

#depth
depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth","meandepth"))
depth<-depth[depth$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,] #use max depth because it's more complete

@@

preds<-analysislakes$lakeinfo[,colnames(analysislakes$lakeinfo) %in% c("lagoslakeid","end","start","nhd_lat")]
preds$tslength<-preds$end-preds$start + 1
preds<-left_join(preds, dt.geo, by="lagoslakeid")
preds<-left_join(preds, dt.conn, by="lagoslakeid")
preds<-left_join(preds, dt.chag, by="hu12_zoneid")
preds<-left_join(preds, dt.lulc, by="lagoslakeid")
preds<-left_join(preds, avg.chla, by="lagoslakeid")
preds<-left_join(preds, cv.accndvi, by="lagoslakeid")
preds<-left_join(preds, depth, by="lagoslakeid")
preds<-left_join(preds, shoredev, by="lagoslakeid")
preds<-left_join(preds, dr, by="lagoslakeid")

@@

rfdat.cohst<-left_join(coh.chlaXaccndvi[,c(10,3)], preds)
rfdat.cohst<-rfdat.cohst[,!colnames(rfdat.cohst) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","nhd_lat")]
rfdat.cohst<-rfdat.cohst[,!grepl("borderhu12s",colnames(rfdat.cohst))]

@@

```{r rfCoherence_lt, echo=TRUE, cache=FALSE}
rfdat.cohlt<-left_join(coh.chlaXaccndvi[,c(10,6)], preds)
rfdat.cohlt<-rfdat.cohlt[,!colnames(rfdat.cohlt) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","nhd_lat")]
rfdat.cohlt<-rfdat.cohlt[,!grepl("borderhu12s",colnames(rfdat.cohlt))]

@@

rfdat.phist<-left_join(coh.chlaXaccndvi[,c(10,2)], preds)
rfdat.phist<-rfdat.phist[,!colnames(rfdat.phist) %in% 
                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid","nhd_lat")]
rfdat.phist<-rfdat.phist[,!grepl("borderhu12s",colnames(rfdat.phist))]

@@

rfdat.philt<-left_join(coh.chlaXaccndvi[,c(10,5)], preds)
rfdat.philt<-rfdat.philt[,!colnames(rfdat.philt) %in% 
                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid","nhd_lat")]
rfdat.philt<-rfdat.philt[,!grepl("borderhu12s",colnames(rfdat.philt))]

@@

## atmosphere/climate is white; land productivity is green; lake productivity is blue; wetlands are brown;
## crops are yellow; other is grey.

print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
ltxt.st<-c("total N deposition","cv(NDVI)","% woody wetlands","all wetlands shoreline","mean runoff",
           "% developed-open space","% regime c wetlands","forest wetlands shoreline","mean annual precipitation",
           "shoreline development ratio")
barcol.st<-c("white","forestgreen","saddlebrown","saddlebrown","white","grey","saddlebrown","saddlebrown","white","royalblue")

print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
ltxt.lt<-c("% shrub/scrub","cv(NDVI)","% regime f wetlands","mean annual precipitation","forest wetlands shoreline",
           "% cultivated crops","headwaters density","% mixed forest", "all wetland shoreline", "% developed-low intensity")
barcol.lt<-c("grey","forestgreen","saddlebrown","white","saddlebrown","forestgreen","grey","forestgreen","saddlebrown","grey")

print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing = T)][1:10])
ltxt.cosphist<-c("open wetlands shoreline","% open wetlands","mean chlorophyll-a","% shrub/scrub",
              "% cultivated crops","% developed-open space","% developed-high intensity",
              "nitrate deposition","groundwater recharge", "% open water")
barcol.st2<-c("saddlebrown","saddlebrown","royalblue","grey","forestgreen","grey","grey","white","royalblue","royalblue")

print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing = T)][1:10])
ltxt.sinphilt<-c("open wetlands shoreline", "all wetlands shoreline","% cultivated crops","% regime f wetlands",
                 "% evergreen forest","forested wetlands shoreline", "% open wetlands","% barren land",
                 "lake max depth","lake connection type")
barcol.lt2<-c("saddlebrown","saddlebrown","forestgreen","saddlebrown","forestgreen","saddlebrown","saddlebrown","grey"
              ,"royalblue","royalblue")

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10_iws_20200609.tif",units="in",
     res=300,width=6.5, height=5)

@@

barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]), col=rev(barcol.st),
        names.arg=rev(ltxt.st),las=2,main="a) Short timescale coher.", horiz=T,font.main=1)

barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]), col=rev(barcol.lt),
        names.arg=rev(ltxt.lt),las=2,main="c) Long timescale coher.", horiz=T, font.main=1)

barplot(rev(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.cosphist),las=2,
        col=rev(barcol.st2), main=expression(paste("b) Short timescale cosine(",phi,")",sep="")), horiz=T)

barplot(rev(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.sinphilt),las=2,
        col=rev(barcol.lt2), main=expression(paste("d) Long timescale sine(",phi,")",sep="")), horiz=T)

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_prep_bywatershed.Rmd
revisions post review

@@

lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x

@@

dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)

accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")

@@

analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
#analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_2.RData")

>>>>

source("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/addAVHRRannualts_bywatershed.R")

@@

lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/lakes20yrs_chla.csv")$x

@@

#dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)

accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
#maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")

@@

lagosIWS<-readOGR("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/IWS/IWS.shp", stringsAsFactors = F)
colnames(lagosIWS@data)[12]<-"lagoslakeid"
lagosIWS<-lagosIWS[lagosIWS$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
lagosIWS<-spTransform(lagosIWS, crs(accndvi))

analysislakes<-addAVHRRannualts_byWatershed(analysislakes, accndvi, watersheds=lagosIWS)
#analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_byWatershed.RData")
